---
format:
  revealjs:
    incremental: false
    css: ../styles.css
    theme: ../theme_medium.scss
execute: 
  echo: true
---

# Day 7: Quarto, Part II

2023-11-14

## Announcements

- **Grades** for all homework assignments are now posted to Moodle

- Keys (answers) for all homework assignments are also posted
  - You can compare your answer to the key

## Recap from Day 6

- Quarto is a system for generating **reports** from **code**

- By using Quarto, we can ensure our results are **reproducible** and derived directly from the data (and code)

## Recap: Working as a team

- To avoid **merge conflicts** (incompatible changes to the same file made by different people) **make a copy** of the final report file **for each team member** to work on.
  - For example, `report-jn.Qmd`

- Share your work by pushing and pulling

- When you are ready to submit the final report, **one person** should edit the final report file `report.Qmd`

- Also submit the repo URL on Moodle as usual

## Due dates

- The report (`report.qmd`) is due **2023-11-20 11:59 PM**

- The presentation will be given in class on **2023-11-21**
  - You can use any software you like to prepare the presentation (such as Powerpoint)
  - Please make sure one team member has their computer ready to show the presentation

## Grading

- Please see the **rubric** in the final report instructions to understand how the paper and presentation will be graded

## Evaluation Sheets

- You will evaluate (score) **each other team's presentation** in class on 2023-11-21
  - Turn in **Form A** (hardcopy) at the end of the class

- You will evaluate the contributions of **each of your team members** after class (due by 2023-11-21 11:59 PM)
  - Turn in **Form B** (digital) on Moodle

# Some tips for your report

## Change the size of a figure

- You can adjust the **size** of the figure with chunk options `fig.height` and `fig.width` (units in inches)

- For example:

```
#| fig.height: 6
#| fig.width: 6
```

## Change the font size

- You can adjust the **overall font size** of the figure like this:

```{r}
#| eval: false
ggplot(gapminder, aes(x = pop, y = lifeExp)) +
  geom_point() +
  theme_gray(base_size = 16)
```

## Change the font size

- You can adjust the **overall font size** of the figure like this:

```{r}
#| eval: false
#| code-line-numbers: "3"
ggplot(gapminder, aes(x = pop, y = lifeExp)) +
  geom_point() +
  theme_gray(base_size = 16)
```

::: {.incremental}

- There are other themes available too, but `theme_gray()` should be fine for the final paper

:::

## Add a pagebreak

- You can add a pagebreak to your document like this:

 <code>&lbrace;&lbrace;</code>`< pagebreak >`<code>&rbrace;&rbrace;</code>

## Group Work

- The rest of the class time is for group work. I will answer any questions you may have about the report.