---
format:
  revealjs:
    incremental: false
    css: ../styles.css
    theme: ../theme_medium.scss
execute: 
  echo: true
---

# Day 8: Quarto, Part II

## Recap from Day 7

- Quarto is a system for generating **reports** from **code**

- By using Quarto, we can ensure our results are **reproducible** and derived directly from the data (and code)

## Due dates

- The report (`report.qmd`) is due **2024-07-24 11:59PM**
  - Push your final commit on GitHub by the deadline
  - Submit **the Word document** on Moodle

- The **evaluation form** is due **2024-07-31 11:59PM**
  - Submit Excel sheet on Moodle

## Grading

- Please see the **rubric** in the final report instructions to understand how the paper will be graded

- You will also **evaluate** each other's final report using the rubric
  - Download the Excel file from Moodle, fill it out, and submit it on Moodle
  - I will post anonymized versions of each report and code to Moodle for you to evaluate

## How to fill out the evaluation form

- Read each report

- Assign a score according to the rubric (1 - 4 points per category)

- Submit the evaluation form (Excel sheet) via Moodle

# Some tips for your report

## Change the size of a figure

- You can adjust the **size** of the figure with chunk options `fig.height` and `fig.width` (units in inches)

- For example:

```
#| fig.height: 6
#| fig.width: 6
```

## Change the font size

- You can adjust the **overall font size** of the figure like this:

```{r}
#| eval: false
ggplot(gapminder, aes(x = pop, y = lifeExp)) +
  geom_point() +
  theme_gray(base_size = 16)
```

## Change the font size

- You can adjust the **overall font size** of the figure like this:

```{r}
#| eval: false
#| code-line-numbers: "3"
ggplot(gapminder, aes(x = pop, y = lifeExp)) +
  geom_point() +
  theme_gray(base_size = 16)
```

::: {.incremental}

- There are other themes available too, but `theme_gray()` should be fine for the final paper

:::

## Add a pagebreak

- You can add a pagebreak to your document like this:

 <code>&lbrace;&lbrace;</code>`< pagebreak >`<code>&rbrace;&rbrace;</code>

## Final report

- The rest of the class time is to work on your final report. I will answer any questions you may have about the report.